\papertitle

### 2013-01-17 manuscript.tex
some edits

We divide our model of the vehicle pose into two independent models for 
simplicity: one for yaw motion, and one for translational motion.

We approximate the yaw dynamics of the ornithopter with a one-dimensional 
model to limit complexity, and because it matches our physical 
implementation. Likewise, we choose the reference heading angle as input to 
the model, and model the dynamics of vehicle and on-board PID controller as 
one system, whose output is the physical heading angle. We show the 
resulting model form in Equation~\ref{eq:plain_model}.
\begin{equation}
\label{eq:plain_model}
H(s) = \frac{K}{1 + Rs}
\end{equation}
To model the translational position of the ornithopter, we use a form of 
Dubin's car model (Eq.~\ref{eq:dubin_car})~\cite{lavalle:planning}, where 
$\phi_{max}$ is the maximum steering angle and $u_{s}$ is the forward speed. 
\begin{equation}
\label{eq:dubin_car}
\begin{aligned}
& \dot{x} = u_{s}sin(\theta)\\
& \dot{y} = u_{s}cos(\theta)\\
& \dot{\theta} = u\\
& u \in U=[-\tan{\phi_{max}},\tan{\phi_{max}}]
\end{aligned}
\end{equation}
We modify this model to treat the angular position $\theta$ as an input 
rather than a state. The overall motion of the system can be modeled as shown 
in Equation~\ref{eq:dubin_car}, where $\theta$ is the time-domain output of 
Equation~\ref{eq:plain_model} with the reference heading angle as input.

@@

We model the pose estimation computation delay, which include the latency of 
updating the particle filter, calculating a new reference attitude, and 
sending the reference attitude command the ornithopter via radio.

@@

The first-order model that we fit to the step response of the onrithopter 
yaw motion is in Equation~\ref{eq:transfer_func}. This model represents the 
tuning dynamics of the ornithopter as well as the PID controller providing 
inputs to the actuators. We present the results of the the step response 
experiment, along with the response of the fitted model, in 
Figure~\ref{fig:step_response}.
\begin{equation}
\label{eq:transfer_func}
H(s) = \frac{0.95}{1+0.62s}
\end{equation}
The step response rise time is 1.4 seconds. The H$^2$Bird flies at an 
average forward velocity of 1.2 m/s during our experiments, so we estimate 
the minimum turning radius of the robot is 1.07 meters, as described in 
Equation~\ref{eq:min_radius}.
\begin{equation}
\label{eq:min_radius}
\begin{aligned}
\text{Minimum radius} & = \frac{360^{\circ}\times\text{Rise time}\times\text{Flight
speed}}{\text{Final angle}\times 2\pi}\\
& = \frac{360^{\circ}\times 1.4s\times 1.2\frac{m}{s}}{90^{\circ}\times2*\pi} = 1.07 m
\end{aligned}
\end{equation}
In the experiments we present in this work, we choose a flight speed lower 
than the maximum speed of the ornithopter, to facilitate more robust 
tracking.

@@

We measured a camera capture latency 40 ms, pose estimation computation 
latency of 12.5 ms, and radio latency of 25 ms.
%----------------------------------------------------------------------------%
\subsection{Model Verification}

@@

\begin{figure*}[tb]
\begin{minipage}[b]{0.45\linewidth}
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\linewidth}
\centering
\centering
\includegraphics[width=\textwidth]{figures/heat_map.png}
\caption{Probability of success for all starting locations. This graphic is 
a result of a Monte Carlo simulation of the reachable set model, in which the 
initial heading of the H$^2$Bird is chosen uniformly at random from $(-90^{\circ},90^{\circ})$.}
\label{fig:heat_map}
\end{minipage}
\end{figure*}

@@

As shown in the figure, there is a region in the middle with a 100\% 
probability of success, which is a subset of the feasible region presented 
in Figure~\ref{fig:feasible_set}. Along the edges of the camera viewing 
triangle, however, the probability of success decreases.

>>>>

We divide our model of the vehicle dynamics into two independent models for 
simplicity: one for yaw motion, and one for translational motion.

We approximate the yaw dynamics of the ornithopter with a one-dimensional 
model to limit complexity, and because it matches our physical 
implementation. Likewise, we choose the reference heading angle as the input to 
the model, and model the dynamics of vehicle and on-board PID controller as 
one system, whose output is the physical heading angle:
\begin{equation}
\label{eq:plain_model}
\begin{aligned}
& H(s) = \frac{K}{1 + Rs}
& \text{where }H(s) = \frac{\theta(s)}{u(s)}
\end{aligned}
\end{equation}
To model the translational position of the ornithopter, we use a form of 
Dubin's car model~\cite{lavalle:planning}: 
\begin{equation}
\label{eq:dubin_car}
\begin{aligned}
& \dot{x} = u_{s}sin(\theta)\\
& \dot{y} = u_{s}cos(\theta)\\
& \dot{\theta} = u\\
& u \in U=[-\tan{\phi_{max}},\tan{\phi_{max}}]
\end{aligned}
\end{equation} 
In the car model, $\phi_{max}$ is the maximum steering angle and $u_{s}$ is
the forward speed. We modify this model to treat the angular position $\theta$
as an input rather than a state. The overall motion of the system can be
modeled as shown in Equation~\ref{eq:dubin_car}, where $\theta$ is the
time-domain output of Equation~\ref{eq:plain_model}, $\theta(t)$, with the
reference heading angle, $u(t)$, as input.

@@

We experienced latency during experiementation in estimating the pose of the
ornithopter on the ground station. Referring to
Figure~\ref{fig:block_diagram}, there were delays in the pose estimation block
while updating the particle filter, in the PID controller block when
calculating the new reference attitude, and in the transmission of the desired
heading from the external controller to the controller on the robot via radio.

@@

The first-order model that we fit to the step response of the onrithopter 
yaw motion is as folows:
\begin{equation}
\label{eq:transfer_func}
H(s) = \frac{0.95}{1+0.62s}
\end{equation}
This model represents the tuning dynamics of the ornithopter as well as the
PID controller providing inputs to the actuators. We present the results of
the the step response experiment, along with the response of the fitted model,
in Figure~\ref{fig:step_response}.

The step response rise time is 1.4 seconds. The H$^2$Bird flies at an 
average forward velocity of 1.2 m/s during our experiments, so we estimate 
the minimum turning radius of the robot is 1.07 meters:
\begin{equation}
\label{eq:min_radius}
\begin{aligned}
\text{Minimum radius} & = \frac{360^{\circ}\times\text{Rise time}\times\text{Flight
speed}}{\text{Final angle}\times 2\pi}\\
& = \frac{360^{\circ}\times 1.4s\times 1.2\frac{m}{s}}{90^{\circ}\times2*\pi} = 1.07 m
\end{aligned}
\end{equation}
In the experiments we present in this work, we choose a flight speed lower 
than the maximum speed of the ornithopter, to facilitate more robust 
tracking.

@@

We measured a camera capture latency of 40 ms, pose estimation computation 
latency of 12.5 ms, and radio latency of 25 ms.
%----------------------------------------------------------------------------%
\subsection{Model Verification}

@@

\begin{figure*}[tb]
\begin{minipage}[t]{0.45\linewidth}
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hfill
\begin{minipage}[t]{0.47\linewidth}
\centering
\centering
\includegraphics[width=\textwidth]{figures/heat_map.pdf}
\caption{Probability of success for all starting locations. This graphic is 
a result of a Monte Carlo simulation of the reachable set model, in which the 
initial heading of the H$^2$Bird is chosen uniformly at random from $(-90^{\circ},90^{\circ})$.}
\label{fig:heat_map}
\end{minipage}
\end{figure*}

@@

As shown in the figure, there is a region in the middle where we had success
in all 40 of the trials, which is a subset of the feasible region presented in
Figure~\ref{fig:feasible_set}. Along the edges of the camera viewing triangle,
however, the probability of success decreases.
